\section{Discussion}

\subsection{Principal Results}
\paragraph{The Hear phase revealed three general areas in which the CHVs were involved in maternal and child health care: home visits with pregnant women and new mothers, monitoring new deliveries in the community, and emergency care. Within each of these areas, three key themes emerged as priorities for the CHVs in designing a new patient management system: the need for fast, easy, data reporting methods, improved communication between CHVs and the clinic regarding referrals, and the need for an effective, reliable way to report and respond to obstetric emergencies. These themes led to the inclusion of five key design features that complemented the daily tasks of CHVs in the study catchment area, which are outlined as follows:}
\begin{enumerate}
	\item Reporting of home visits through IVR
	\item Notification of referred patients visiting the clinic through text message
	\item Reporting of deliveries through IVR
	\item Notification of patients delivering at the clinic through text message
	\item Reporting of emergencies directly to the clinic through IVR
\end{enumerate}

\paragraph{Mock testing of these features during the Create phase revealed enthusiasm and satisfaction with the service, but concerns were raised regarding the ability for CHVs to flash the Baby Monitor phone number should they run out of phone credit. This issue was addressed by including m-Pesa payments, which can be transferred directly into phone credit, for CHVs participating in the study.}

\paragraph{CHVs generally found the system to be usable. The text messages notifying CHVs of patient visits and deliveries were among the highest rated features of the system. }\todo{This section to be updated once results are complete. - A}

\subsection{Limitations}
This study piloted an intervention that was previously untested in this target population. Thus, the scope of the study was limited to a single clinic and a small, convenience sample of CHVs working in the clinic's catchment area. Participants for focus groups were selected based on English comprehension and demonstrated interest in the study, and thus may not generally represent the perspectives or viewpoints of all other CHVs within the health system. Due to time contraints, only one cycle of the Hear and Create phases were completed; in future iterations, additional cycles of prototyping and mock testing would have been conducted in order to refine and create additional features for the system.  

\subsection{Comparison with Prior Work}

- MoTECH program: IVR/texts in Ghana for midwives
- Believe that this has potential to improve community-based maternal and child health care

\subsection{Conclusions}